---
title: "figure3_semantic_heatmap"
author: "KCM"
date: "2022-09-01"
output: 
  html_document: default
  word_document: default
  pdf_document: default
code_folding: hide
---
```{r global-options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

<style>
body {
text-align: justify}
</style>

```{r eval=!exists(".standalone"), message=FALSE, include=!exists(".standalone")}
plotDir = ifelse(exists(".standalone"), "", "part1/")
if(plotDir!="") if(!file.exists(plotDir)) dir.create(plotDir)
knitr::opts_chunk$set(fig.path=plotDir, dev=c("png", "pdf"))
knitr::opts_chunk$set(dpi=600,fig.width=15,fig.height = 10)


library(IOBR)
library(EPIC)
library(estimate) 
library(tidyverse)
library(tidyHeatmap)
library(maftools)
library(ggpubr)
library(ggplot2)
library(survival)
library(kableExtra)
```


## Read expression and metadata
```{r Expression_metadata}
df = read.csv("High_gene_TPM_cibersort.txt",sep = "\t",row.names = 1,check.names = FALSE)

metadata = read.csv("..//Cibersort_meta.txt",sep = "\t")

meta_dat1 = metadata %>% select(patient,Risk_Cyto,FAB,SURVIVAL_STATUS,SURVIVAL_MONTH,prior_malignancy)
names(meta_dat1)[1] = "ID"

#TCGA-AB-2895
#TCGA-AB-2946
#TCGA-AB-2810
f <- c("TCGA-AB-2895","TCGA-AB-2946","TCGA-AB-2810")


#Syntax to drop columns using %in% operator
eset_stad <- df[ , !names(df) %in% f]

meta_dat<- meta_dat1[!grepl("N.D.", meta_dat1$Risk_Cyto),]

```


## Calculate TME associated signatures-(through PCA method).

```{r TME}
sig_tme<-calculate_sig_score(pdata           = NULL,
                             eset            = eset_stad,
                             signature       = signature_tme,
                             method          = "pca",
                             mini_gene_count = 2)

sig_tme %>%
  kable() %>%
  kable_styling()

write_tsv(sig_tme,"TME_signature.txt")

```


## Estimate TME associated signatures-(through ssGSEA method).

```{r Ig_tme}
ig_tme<-calculate_sig_score(pdata           = NULL,
                            eset            = eset_stad,
                            signature       = signature_tme,
                            method          = "ssgsea",
                            mini_gene_count = 5)
ig_tme %>%
  kable() %>%
  kable_styling()

```


## Evaluate metabolism related signatures.

```{r metabolism}

sig_meta<-calculate_sig_score(pdata           = NULL,
                              eset            = eset_stad,
                              signature       = signature_metabolism,
                              method          = "pca",
                              mini_gene_count = 2)
sig_meta %>%
  kable() %>%
  kable_styling()

```


## Analyze all collected signature scores (integrating three methods: PCA, ssGSEA and z-score).
```{r Three_method_integration}
sig_res<-calculate_sig_score(pdata           = NULL,
                             eset            = eset_stad,
                             signature       = signature_collection,
                             method          = "integration",
                             mini_gene_count = 2)
sig_res  %>%
  kable() %>%
  kable_styling()

```

## The signature gene sets derived from GO, KEGG, HALLMARK and REACTOME datasets.

```{r Ontology}
sig_hallmark<-calculate_sig_score(pdata           = NULL,
                                  eset            = eset_stad,
                                  signature       = hallmark,
                                  method          = "ssgsea",
                                  mini_gene_count = 2)
sig_hallmark %>%
  kable() %>%
  kable_styling()
write_tsv(sig_hallmark,"Ontology_hallmark_signature.txt")

```


## Method 1: CIBERSORT
```{r CIBERSORT}
cibersort<-deconvo_tme(eset = eset_stad, method = "cibersort", arrays = FALSE, perm = 500)
#res<-cell_bar_plot(input = cibersort[1:20,], title = "CIBERSORT Cell Fraction")
write_tsv(cibersort,"CIBERSORT_signature.txt")

```


## Method 2: EPIC

```{r EPIC}
epic<-deconvo_tme(eset = eset_stad, method = "epic", arrays = FALSE)

```

## Method 3: MCPcounter

```{r MCPcounter}
mcp<-deconvo_tme(eset = eset_stad, method = "mcpcounter")
#head(mcp)
```


## Method 4: xCELL


```{r xCELL}
#xcell<-deconvo_tme(eset = eset_stad, method = "xcell",arrays = FALSE)

```


## Method 5: ESTIMATE
```{r ESTIMATE}
estimate<-deconvo_tme(eset = eset_stad, method = "estimate")
write_tsv(estimate,"estimate_signature.txt")

```


##  Method 7: quanTIseq

```{r quanTIseq}
quantiseq<-deconvo_tme(eset = eset_stad, tumor = TRUE, arrays = FALSE, scale_mrna = TRUE, method = "quantiseq")

#res<-cell_bar_plot(input = quantiseq[1:12, ], title = "quanTIseq Cell Fraction")
```



## Method 8: IPS

```{r IPS}
ips<-deconvo_tme(eset = eset_stad, method = "ips", plot= FALSE)

```

##  Combination of above deconvolution results

```{r Combine_signature}
tme_combine<-cibersort %>% 
  inner_join(.,mcp,by = "ID") %>% 
  inner_join(.,epic,by      = "ID") %>% 
  inner_join(.,estimate,by  = "ID") %>% 
  #inner_join(.,timer,by     = "ID") %>% 
  inner_join(.,quantiseq,by = "ID") 
dim(tme_combine)
```
## Metadata_comibine 

```{r sign_1}
pdat_map = inner_join(meta_dat,tme_combine[c(1)])
pdata_group<- meta_dat

res1<-iobr_cor_plot(pdata_group           = pdata_group,
                   id1                   = "ID",
                   feature_data          = tme_combine,
                   id2                   = "ID",
                   target                = NULL,
                   group                 = "FAB",
                   is_target_continuous  = FALSE,
                   padj_cutoff           = 1,
                   index                 = 1,
                   category              = "signature",
                   #signature_group       = tme_combine[c(1,3,5)],
                   ProjectID             = "IMvigor210",
                   palette_box           = "paired1",
                   palette_corplot       = "pheatmap",
                   palette_heatmap       = 2,
                   feature_limit         = 26,
                   character_limit       = 30,
                   show_heatmap_col_name = FALSE,
                   show_col              = FALSE,
                   show_plot             = TRUE,
                   path                  = "1-BOR-relevant-signatures",)
```



## Sign2

```{r Sign2}
# pdata_group1 <- pdata_group %>%  remove_rownames() %>%
#   column_to_rownames(var = 'ID')

#ef <- t(eset_stad)


res<-iobr_cor_plot(pdata_group           = pdata_group,
                   id1                   = "ID",
                   feature_data          = eset_stad,
                   id2                   = "ID",
                   target                = NULL,
                   group                 = "signature",
                   is_target_continuous  = FALSE,
                   padj_cutoff           = 1,
                   index                 = 2,
                   category              = "gene",
                   signature_group       = signature_collection[c(1:2,4)],    
                   ProjectID             = "IMvigor210",
                   palette_box           = "paired1",
                   palette_corplot       = "pheatmap",
                   palette_heatmap       = 4,
                   feature_limit         = 26,
                   character_limit       = 30,
                   show_heatmap_col_name = FALSE,
                   show_col              = FALSE,
                   show_plot             = TRUE)

```


## gene signature single gene 

```{r PARP3}
# pdata_group3 <-pdata_group2 %>% select(ID,RDM1,PARP3) %>% as.data.frame()
# 
# res2<-iobr_cor_plot(pdata_group           = pdata_group3,
#                    id1                   = "ID",
#                    feature_data          = tme_combine,
#                    id2                   = "ID",
#                    target                = "PARP3",
#                    #group                 = "group1",
#                    is_target_continuous  = TRUE,
#                    padj_cutoff           = 1,
#                    index                 = 1,
#                    category              = "signature",
#                    #signature_group       = sig_group[1],
#                    #ProjectID             = "IMvigor210",
#                    palette_box           = "set2",
#                    palette_corplot       = "pheatmap",
#                    palette_heatmap       = 2,
#                    feature_limit         = 26,
#                    character_limit       = 30,
#                    show_heatmap_col_name = FALSE,
#                    show_col              = FALSE,
#                    show_plot             = TRUE,
#                    path                  = "3-HCP5-relevant-signatures")
```











