---
title: "MOFA_enrichment_high"
author: "KCM"
date: "2022-09-01"
output: 
  html_document: default
  word_document: default
  pdf_document: default
code_folding: hide
---
```{r global-options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

<style>
body {
text-align: justify}
</style>

```{r eval=!exists(".standalone"), message=FALSE, include=!exists(".standalone")}
plotDir = ifelse(exists(".standalone"), "", "part1/")
if(plotDir!="") if(!file.exists(plotDir)) dir.create(plotDir)
knitr::opts_chunk$set(fig.path=plotDir, dev=c("png", "pdf"))
knitr::opts_chunk$set(dpi=600,fig.width=15,fig.height = 10)
##reticulate::conda_install(c("mofapy2"),envname = "mofa_tool", pip = TRUE)
#https://levelup.gitconnected.com/multi-omics-analysis-3857956a7a3d
#library(MOFAdata)
library(data.table)
library(ggplot2)
library(tidyverse)
library(reticulate)
use_condaenv(condaenv = "mofa_tool")
library(MOFA2)
library(MOFAdata)
#library(mofaCLL)
library(survminer)
library(maxstat)
library(gridExtra)
library(cowplot)
library(survival)






```



# Prepare MOFA object
```{r data_overview}
AML_metadata = read.csv("..//map_144_metadata.txt",sep = "\t")
 
 RNA_seq <- read.table("..//Low_hig_gene/rna_seq_gene_methyl_greater_thn_one.txt",sep = "\t",strip.white = FALSE,check.names = FALSE,header=TRUE,row.names = 1)
 #head(RNA_seq)
 class(RNA_seq)
 Methylation <- read.table("..//Low_hig_gene/High_std_expr_probe.txt",sep = "\t",strip.white = FALSE,check.names = FALSE,header=TRUE,row.names = 1)
 #head(Methylation)
dd <- Methylation
 #https://stackoverflow.com/questions/9977686/how-to-remove-rows-with-any-zero-value
 row_sub = apply(dd, 1, function(row) all(row !=0 ))
 ##Subset as usual
 d1 <- dd[row_sub,]
 
 #RNA_seq  <- RNA_seq[,genomic_idx2]
 #genomic_idx1 <- match(rownames(AML_metadata), colnames(d1))
 #Meth_seq <- d1[,genomic_idx1]
# library("mixOmics")
 #https://nbisweden.github.io/workshop_omicsint_ISMBECCB/session_ml/UnsupervisedOMICsIntegration/UnsupervisedOMICsIntegration.html
 #scBSseq <- Meth_seq
 #my_nearZeroVar<-nearZeroVar(as.data.frame((scBSseq)))
 #head(my_nearZeroVar$Metrics)
 
 d1$variance = apply(d1, 1, var)
 data2 = d1[d1$variance >= quantile(d1$variance, c(.70)), ] #50% most variable genes
 data2$variance <- NULL
 dim(data2)
 
 
 omics <- list( 
                  mRNA = as.matrix(RNA_seq),
                  #Mutations = gene, 
                  Methylation = as.matrix(data2))
 
  MOFAobject <- create_mofa_from_matrix(omics)
plot_data_overview(MOFAobject)
 
```



## Train Model

```{r train_model}


#Define data options
# data_opts <- get_default_data_options(MOFAobject)
# head(data_opts)
# 
# #Define model options
# model_opts <- get_default_model_options(MOFAobject)
# head(model_opts)
#  
# #Define train options
# train_opts <- get_default_training_options(MOFAobject)
# head(train_opts)


#Build and train the MOFA object
# MOFAobject <- prepare_mofa(
#   object = MOFAobject,
#   data_options = data_opts,
#   model_options = model_opts,
#   training_options = train_opts
# )
#  
# 
# MOFAobject <- run_mofa(MOFAobject, outfile="Expression_methylation_MOFA/Lwo_gene.hdf5")
# saveRDS(MOFAobject,"Lwo_gene.rds")

MOFAobject <- readRDS("..//High_gene.rds")


 names(AML_metadata)[1] = "sample"
 
 samples_metadata(MOFAobject) <- AML_metadata
```

## Factor correlation

```{r Factor_correlation}

plot_factor_cor(MOFAobject)

#r2$r2_total
#r2$r2_per_factor
```



## Variance explained

```{r Variance_explained}
plot_variance_explained(MOFAobject, plot_total = T)[[2]]

plot_variance_explained(MOFAobject, x="view", y="group", factors=1:3)
```


## Factor variance explained
```{r Factor_variance}
plot_variance_explained(MOFAobject, max_r2=70)


```

## Gene weight

```{r gene_loadings}
plot_top_weights(MOFAobject,
  view = "mRNA",
  factor = 1,
  nfeatures = 40
)

```

## Factor and weights
```{r Factor_Weights}
weights <- get_weights(MOFAobject, as.data.frame = TRUE,factors = 2,views = "Methylation")
head(weights, n=3)


factors <- get_factors(MOFAobject, as.data.frame = TRUE)
head(factors, n=3)


data <- get_data(MOFAobject, as.data.frame = TRUE)
head(data, n=3)
```


## Scatter 


```{r Scatter_negative_postive}
plot_data_scatter(MOFAobject,
  view = "mRNA",         # view of interest
  factor = 1,sign = "negative",             # factor of interest
  features = 10,           # number of features to plot (they are selected by weight)
  add_lm = TRUE,          # add linear regression
  color_by = "RISK_CYTO",
  dot_size = 1.2
)

plot_data_scatter(MOFAobject,
  view = "mRNA",         # view of interest
  factor = 1,sign = "positive",             # factor of interest
  features = 10,           # number of features to plot (they are selected by weight)
  add_lm = TRUE,          # add linear regression
  color_by = "RISK_CYTO",
  dot_size = 1.2
)

```





## Probe weight
```{r probe_loadings}
plot_top_weights(MOFAobject,
  view = "Methylation",
  factor = 1,
  nfeatures = 40
)


```






## Factor visualisaation
```{r FACTOR_PCA}
plot_factor(MOFAobject, 
  factor = 1:7,
  color_by = "FAB",
  shape_by = "RISK_CYTO"
)
```

## Factor desity plot

```{r Factor_density_plot}
plot_factors(MOFAobject, 
  factors = 1:3,
  color_by = "RISK_CYTO"
)
```


## Weight of all factors

```{r Weigh_factors}
allWeights <- get_weights(MOFAobject,
                         views = "all",
                         factors = "all",
                         as.data.frame = TRUE) %>% as.tibble()

allFactors <- get_factors(
  MOFAobject, 
  factors = "all",
  as.data.frame = TRUE
) %>% as.tibble()

Factor_subset = AML_metadata %>% select(sample,RISK_CYTO,FAB,OS,Status)

allFactors1 <- inner_join(allFactors,Factor_subset)

```


## Separation by factors

```{r Separation_Factors}
plotTab <- filter(allFactors1, factor %in% c("Factor3","Factor4")) %>%
  spread(key =factor, value = value) %>% mutate(FAB = factor(FAB))
p <- ggplot(plotTab, aes(x=Factor3, y=Factor4, color = FAB, 
                         shape = RISK_CYTO, label = sample,siz)) + 
  geom_point(aes(size = 1.2)) 
  #scale_shape_manual(values = c(M = 16, U =1))
p

```


## Plot_heatmap_mrna
```{r mrna_heatmap}
plot_data_heatmap(MOFAobject,
                  view = "mRNA",         # view of interest
                  factor = 2,             # factor of interest
                  features = 90,          # number of features to plot (they are selected by weight)
                  
                  # extra arguments that are passed to the `pheatmap` function
                  cluster_rows = TRUE, cluster_cols = TRUE,
                  show_rownames = TRUE, show_colnames = FALSE,annotation_samples = "RISK_CYTO"
)



```


## methylation heatmap
```{r}
plot_data_heatmap(MOFAobject,
                  view = "Methylation",         # view of interest
                  factor = 2,             # factor of interest
                  features = 90,          # number of features to plot (they are selected by weight)
                  
                  # extra arguments that are passed to the `pheatmap` function
                  cluster_rows = TRUE, cluster_cols = TRUE,
                  show_rownames = TRUE, show_colnames = FALSE,annotation_samples = "RISK_CYTO"
)
```







## Survival

```{r survial_factor}
survT <- Factor_subset
names(survT)[5] = "died"
```

## Survial cox function

```{r Cox_function}
com <- function(response, time, endpoint, scale =FALSE) {  
  
  if (scale) {
    #calculate z-score
    response <- (response - mean(response, na.rm = TRUE))/sd(response, na.rm=TRUE)
  }
  surv <- coxph(Surv(time, endpoint) ~ response) 
  
  
  tibble(p = summary(surv)[[7]][,5], 
         HR = summary(surv)[[7]][,2], 
         lower = summary(surv)[[8]][,3], 
         higher = summary(surv)[[8]][,4])
}
```


## HR ratio cox

```{r Cox_hazard}
testTab <- left_join(allFactors1, survT)

#for OS
resOS <- filter(testTab, !is.na(OS)) %>%
  group_by(factor) %>%
  do(com(.$value, .$OS, .$died, TRUE)) %>% ungroup() %>%
  arrange(p) %>% mutate(p.adj = p.adjust(p, method = "BH")) %>%
  mutate(Endpoint = "OS")

#resOS

plotTab <- resOS %>%
 filter(factor %in% c("Factor3","Factor7","Factor14"))
  
haPlot <- ggplot(plotTab, aes(x=factor, y = HR, col = Endpoint, dodge = Endpoint)) + 
  geom_hline(yintercept = 1, linetype = "dotted") +
  geom_point(position = position_dodge(width=0.8)) +
  geom_errorbar(position = position_dodge(width =0.8), 
                aes(ymin = lower, ymax = higher), width = 0.3, size=1) + 
  geom_text(position = position_dodge2(width = 0.8),
            aes(x=as.numeric(as.factor(factor))+0.15,
                label = sprintf("italic(P)~'='~'%s'",
                                formatNum(p))),
            color = "black",size =5, parse = TRUE) +
  xlab("Factor") + ylab("Hazard ratio") +
  scale_y_log10(limits = c(0.5,4)) +
  coord_flip() + theme_full + theme(legend.title = element_blank(),
                                    legend.position = c(0.2,0.1),
                                    legend.background = element_blank(),
                                    legend.key.size = unit(0.5,"cm"),
                                    legend.key.width = unit(0.6,"cm"),
                                    legend.text = element_text(size=rel(1.2))) +
  scale_color_manual(values = c(OS = colList[3], TTT = colList[5])) 

#haPlot



```


## KMplot

```{r KM_plot}
facList <- sort(filter(resOS, p.adj <=0.06)$factor)
osList <- lapply(facList, function(x) {
  eachTab <- filter(testTab, factor == x) %>%
    select(value, OS, died) %>% filter(!is.na(OS))
  pval <- filter(resOS, factor == x)$p
  km(eachTab$value, eachTab$OS, eachTab$died, sprintf("%s VS Overall survival time", x),
     stat = "maxstat", pval = pval, showTable = TRUE)
})

grid.arrange(grobs = osList, ncol = 2)
```


## Filter factors

```{r Factor_filter}
# facTab <- filter(allFactors1, factor == "Factor1")
# 
# facTab
# 
# LDT <- AML_metadata %>% mutate(F4 = facTab[match(patID, facTab$sample),]$value) %>%
#   filter(!is.na(F4)) %>%
#   mutate(IGHV = as.factor(facTab[match(patID, facTab$sample),]$IGHV))
# corRes <- cor.test(log10(LDT$doubling.time), LDT$F4)
```






